Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-04 paper.tex
Add tropopause height to stability budget figures to aid in discussion of physical processes.

%FIGURE 2%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).}
\label{fig:mod+bud+res}
\end{figure}

@@

%FIGURE 4%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/n2-24hr-avgs.png}}
\caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
Orange lines represent the cold-point tropopause averaged over the same time periods.}
\label{fig:n2-24hr-avgs}
\end{figure*}

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
\end{figure*}
\begin{figure}
\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.}
\label{fig:stab-00-24}
\end{figure}

@@

%FIGURE A1%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa. Orange lines represent the cold-point tropopause averaged over the same time periods.}
\label{fig:n2-1000km}
\end{figure*}

%FIGURE A2%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab.}
\label{fig:turb-50m}
\end{figure*}

>>>>

%FIGURE 2%
\begin{figure}[ht]
\centerline{\includegraphics[width=39pc]{figures/mod+bud+res.png}}
\caption{Left panels: Twenty-four-hour changes in squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) computed using Eq.~\ref{eq:modelchange} over (top row) 0-24 hours, (middle row) 24-48 hours, (bottom row) 48-72 hours.
Middle Panels: The $N^2$ change over the same time periods computed using Eqs. \ref{eq:dn2dt}-\ref{eq:budgetchange}, %together with Eqs. \ref{eq:dn2dt}, \ref{eq:dthetadt}.
Right Panels: The budget residual over the same time periods, computed by subtracting the budget change (middle column) from the model change (left column).
Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:mod+bud+res}
\end{figure}

@@

%FIGURE 4%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/n2-24hr-avgs.png}}
\caption{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours.
Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:n2-24hr-avgs}
\end{figure*}

%FIGURE 5%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/h000-h024-budgetterms.png}}
\end{figure*}
\begin{figure}
\caption{(a) Total change in $N^2$ over the 0-24-hour period (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) and the contributions to that change from (b) the sum of horizontal and vertical advection, (c) vertical turbulence, (d) longwave and shortwave radiation, (e) the sum of horizontal advection, vertical advection, and vertical turbulence, and (f) the sum of horizontal advection, vertical advection, vertical turbulence, and longwave and shortwave radiation.
Orange lines represent the cold-point tropopause height averaged over the 0-24-hour period.}
\label{fig:stab-00-24}
\end{figure}

@@

%FIGURE A1%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/n2-1000km.png}}
\appendcaption{A1}{Twenty-four-hour averages of squared Brunt-V{\"a}is{\"a}l{\"a} frequency ($N^2$; 10\textsuperscript{-4} s\textsuperscript{-2}) over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Aa. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:n2-1000km}
\end{figure*}

%FIGURE A2%
\begin{figure*}[ht]
\centerline{\includegraphics[width=39pc]{figures/turb-50m.png}}
\appendcaption{A2}{The contribution of vertical turbulence to the $N^2$ variability (10\textsuperscript{-4} s\textsuperscript{-2} (24 h)\textsuperscript{-1}) averaged over (a) 0-24 hours, (b) 24-48 hours, (c) 48-72 hours, and (d) 72-96 hours for the simulation described in Appendix Ab. Orange lines represent the cold-point tropopause height averaged over the same time periods.}
\label{fig:turb-50m}
\end{figure*}
